Structuring College Access

### 2025-02-17 index.qmd
add maps to slides

@@

      # -------------------------------------------
      # ADDITIONAL: race_by_firstgen for each order
      # -------------------------------------------
      # Like the column approach, one slide per order_id
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num, rq_num, " {.hide}"))
        # Filenames look like:
        #   rq2_northern_new_jersey_order_448922_race_by_firstgen.png
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = rq, metro = m, graph_type = graph_type_rbf)
      }

>>>>

      # Add RQ1 map
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines("#### Map")

      rq1_map <- if_else(
        m == 'los angeles',
        'https://rq1-map-los-angeles.netlify.app',
        str_c('./results/maps/rq1_map_', str_replace_all(m, " ", "_"), '.html')
      )

      writeLines(str_c('<iframe data-src="', rq1_map, '" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))

@@

      # -------------------------------------------
      # ADDITIONAL: race_by_firstgen for each order
      # -------------------------------------------
      # Like the column approach, one slide per order_id
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num, " {.hide}"))
        # Filenames look like:
        #   rq2_northern_new_jersey_order_448922_race_by_firstgen.png
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = rq, metro = m, graph_type = graph_type_rbf)
      }

      # Add RQ2 map
      writeLines(str_c("### Research question ", rq_num, " {.hide}"))
      writeLines("#### Map")

      writeLines(str_c('<iframe data-src="./results/maps/rq2_map_', str_replace_all(m, " ", "_"), '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))
